Detection and replication of epistasis influencing transcription in humans

### 2013-09-13 docs/manuscript/manuscript.tex
updated response to reviewers

\documentclass{article}
\usepackage[superscript,biblabel]{cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage{authblk}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{lineno}

\makeatletter
\renewcommand\AB@affilsepx{. \protect\Affilfont}
\makeatother
\linenumber

@@

In addition, using the meta analysis from the replication samples only, we observed that 316 of the remaining 404 discovery SNP pairs had replication interaction $p$-values more extreme than the 2.5\% confidence interval of the quantile-quantile plot against the null hypothesis of no interactions ($p << 1.0 \times 10^{-16}$, Figure \ref{fig:qqMeta} and Supplementary Figure \ref{fig:qqMetaNonsig}). Concordance of the direction of the effect of the largest variance component was also highly significant ($p = 5.71 \times 10^{-31}$, Supplementary Table \ref{tab:sign}). The congruence of the epistatic networks in discovery and replication datasets is shown in Figure \ref{fig:fireworks}, demonstrating that these complex genetic patterns are common even across independent datasets. A further replication was attempted using the Centre for Health Discovery and Wellbeing (CHDWB) dataset \cite{Preininger2013}, but only 20 of the SNP pairs passed filtering because the sample size was small ($n=139$), and likely due to insufficient power we found no evidence for replication (Supplementary Figure \ref{fig:qqgg}).

>>>>

\documentclass{article}
\usepackage[superscript,biblabel]{cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage{authblk}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{lineno}
\linenumbers

\makeatletter
\renewcommand\AB@affilsepx{. \protect\Affilfont}
\makeatother

@@

In addition, using the meta analysis from the replication samples only, we observed that 316 of the remaining 404 discovery SNP pairs had replication interaction $p$-values more extreme than the 2.5\% confidence interval of the quantile-quantile plot against the null hypothesis of no interactions where $p$-values are assumed to be uniformly distributed ($p << 1.0 \times 10^{-16}$, Figure \ref{fig:qqMeta} and Supplementary Figure \ref{fig:qqMetaNonsig}). Concordance of the direction of the effect of the largest variance component was also highly significant ($p = 5.71 \times 10^{-31}$, Supplementary Table \ref{tab:sign}). The congruence of the epistatic networks in discovery and replication datasets is shown in Figure \ref{fig:fireworks}, demonstrating that these complex genetic patterns are common even across independent datasets. A further replication was attempted using the Centre for Health Discovery and Wellbeing (CHDWB) dataset \cite{Preininger2013}, but only 20 of the SNP pairs passed filtering because the sample size was small ($n=139$), and likely due to insufficient power we found no evidence for replication (Supplementary Figure \ref{fig:qqgg}).
